Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis

### 2019-09-06 ecoapp-comments/response.txt

Dear Ecological Applications editorial staff and reviewers,

We appreciate your thorough review of our manuscript, "Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis." We are pleased to present a significantly revised version of the manuscript, which we feel has improved significantly since the last version, in large part thanks to the reviewers' thoughtful and helpful comments and suggestions. A summary of the major changes in this revision is as follows:

First, and most importantly, we have re-written virtually all of the results and discussion concerning the scale dependence of leaf economic relationships. We now organize both of these sections around three groups of traits that show varying degrees of consistency with the global leaf economic spectrum: Morphological and biochemical traits (SLA, N, and P), for which these relationships are most robust; metabolic traits (R_d, V_{c,max}, J_{max}), for which they are somewhat more variable; and leaf lifespan, for which they are even more variable. We have also replaced the 2 figures related to this topic---the previous Figures 2 and 3---with a new Figure 1 that should be easier to read and which better shows the major features of our results.

Second, we have re-organized the introduction to better set up the need and ecological context for our analysis. We now begin with a discussion of trait covariance in general and of the global leaf economic spectrum specifically. We then provide a brief overview of evidence for deviations from the leaf economic spectrum at smaller scales. We then briefly discuss the challenges with working with individual species from a modeling perspective, which leads to a paragraph introducing plant functional types. This leads us to our guiding question about whether the leaf economic spectrum holds at the PFT scale.

Finally, following the request of Reviewer 1, we have performed a cross-validation of our approach to trait imputation. This analysis provides a more robust comparison of the three models we tried, and serves as a validation of our imputation approach, which is important given the massive volume of imputation performed in this analysis.

In addition to these changes, we have addressed many concerns and suggestions of the reviewers about specific lines of text, aesthetic choices, etc.

Thank you in advance for your consideration of this revised manuscript!

(NOTE: All line numbers below refer to the document with changes highlighted.)

1 Reviewer 1
============

        a) at several crucial places in the ms, the authors interpret a reduction of posterior uncertainty essentially as an improvement of model fit. Although I would agree that this pattern is indicative of a better fit, it is not a direct proof, and it is possible to have counterexamples. To resolve this issue, the authors should explicitly assess model fit (e.g. calculate RMSE or similar either on the fitted data, or a hold-out), and replace this in the discussion appropriately.

We have added a 20-fold cross-validation exercise comparing the ability of the grouped univariate, multivariate, and hierarchical models to impute trait values. This analysis is described on lines 289-292, and the results are shown in the new Fig. 3, described on lines 410-417, and briefly discussed in lines 554-555. We also revised phrasing throughout the manuscript to the more precise "reduced predictive uncertainty".

        b) The paper itself is written comparatively well, but motivation and ecological interpretation could be extended at some points. See my detailed remarks.

  We have re-written large parts of the introduction to address this concern, with particular emphasis on the need for PFTs in the context of trait ecology and vegetation modeling. We have also heavily revised the results (section 3.1 throughout) and discussion (section 4.1 throughout) concerning within- vs. across-PFT covariance patterns to better highlight overarching ecological patterns. Specifically, we divided the seven traits in this analysis into three groups with varying degrees of consistency for leaf economic relationships: Morphological and biochemical traits (SLA, N, and P) show the most robust relationships; metabolic traits (R_d, V_{c,max}, J_max) show slightly less robust relationships; and leaf lifespan shows the least consistent relationships.

        c) The choice to structure species by PFTs seems obvious from the perspective of a person working with dynamic vegetation models, but less obvious from a general ecology / data analysis perspective. If we forget the models for a moment, I am quite sure that there are other grouping options that might make sense, maybe more sense, other than a PFT grouping. Some things that come to mind is

        - Group species according to taxonomy
        - Group species according to traits (have to make sure
          that this doesn’t become circular)
        - Group species according to space / habitat / ecosystem
        - Fit species grouping with the model (could also consider
          unsupervised classification according to some objective)

        I think the authors should at least consider and discuss these options in the paper as a possibility for further research. Personally, I think adding some of these analyses would make a much stronger and more general paper, but I hesitate to make this a requirement, as this would shift the focus of the paper and would probably require significant rewriting of intro and discussion as well.

  We agree that exploring other species groupings, including those suggested here, would be an interesting future direction for this work, and we have added text to this effect to the discussion (lines 584-587). However, we have chosen to keep this paper focused on groupings by plant functional type, primarily because these rules are relevant, and can be used as inputs, to dynamic vegetation models.

        2 Abstract goes directly into the topic. A bit of motivation / relevance would be nice.

  We have added two sentences introducing the leaf economic spectrum and its study at different scales to the abstract (lines 2-5).

        8 indicating … -> Spontaneously, I don’t see how this can be concluded, but I’ll read on and wait to be educated

  We have removed this sentence from the revised introduction, so this comment no longer applies.

        13 I was again missing a conclusion about the relevance / applicability of the findings

  We have revised the abstract accordingly to better highlight the ecological implications of our results (lines 13-19, 21-24, 27-29).

        15 Personally, I would have found it more logical to start this paper with trait correlations and the LES, because this is what you examine in the end, and then follow up with the PFTs

  We have re-organized the introduction in accordance with this comment. We now start with a discussion of the leaf economic spectrum, then move to empirical evidence of and mechanisms for local-scale deviations from it, and eventually arrive at why PFTs are a useful intermediate scale for this study.

        17 Why "however". There doesn’t seem to be a contradiction. It’s more: at the same time

        19 Benefits … most papers cited here just demonstrate the fact that there is variability and speculate about the benefits, but OK …

  We have rewritten this part of the introduction, so this comment no longer applies.

        23 could make a paragraph break here

  In the original draft, we agree that this would have made sense. However, in the revised version, this entire paragraph is shorter, and this sentence is a natural continuation of the previous point, so we have not added a break.

        24 It’s a bit weird to say the allometry constrains the
        traits, as the allometry can be said to be a trait itself.
        I guess what you mean is that there are relationships
        between traits, so that trait-space can be reduced.

  We have replaced "allometries" with "biophysical limitations", and clarified the first half of this sentence to refer specifically to "variability in plant functional traits" (lines 42-43).

        29 erase well

  We have revised this accordingly (line 50).

        31 causality probably goes both ways – in particular climates, you find particular parts of the LES, although there may also be plasticity

  We agree, and have replaced "influenced by" with "related to" (line 54).

        35 could also cite Scheiter, Simon, Liam Langan, and Steven I. Higgins. "Next‐generation dynamic global vegetation models: learning from community ecology." New Phytologist 198, no. 3 (2013): 957-969.

  We have added this reference (line 57).

        51 Here and for the other points above: I agree with the conclusions summarized here, but it might be helpful for the reader to provide a very short sketch of the premises / arguments for the respective conclusions in the cited papers. E.g. what’s the argument in Messier 2016 for the causality problem?

  In our re-organization of the introduction, we ended up dropping the specific sentence to which this is referring.

        51 Also, the Messier paper is 2017, not 2016

  We have revised this reference everywhere it occurs.

        53 OK, but why is that a problem for using global trait correlations?

  In our re-organization of the introduction, we ended up dropping the specific sentence to which this is referring (line 84).

        59 I get the assembly point, this is basically about transient dynamics through dispersal limitation, but isn’t the larger concern if the potential trait space / trade-off is actually much larger / different than what we see as being “filtered by evolution”.

  In our re-organization of the introduction, we ended up dropping the specific sentence to which this is referring (lines 88-91).

        60 An issue with this entire section that ends here is that it doesn’t become clear which of the issues you discuss here (if any) can be solved by an approach where you fit trait correlations in hierarchical groups. The arguments in favor of the PFT analysis in the following paragraph make sense to me, but they relate only vaguely to the specific issues in the previous section. Please be more clear about which issues are solved by working with PFTs (and why), and which remain unsolved.

  We have re-organized and re-written the introduction to address this and related concerns. In the revised version, there is a more logical argument flow: (1) Global trait correlations may not hold at local scales (lines 60-72). (2) But, trying to do ecosystem ecology from the bottom-up starting with individual species is also problematic (lines 96-104). (3) Therefore, PFTs are a useful intermediate scale (lines 105-125).

        78 What do you mean by constrain? Predict? See also my major comment: what’s the performance criterion under which you want to evaluate an “improvement”.

  We have clarified this by replacing "constrain" with "reduce uncertainties in" (line 130). We address the broader concern about model fit in the main response.

        109 Seems obvious that one could also try this analysis on taxonomic groups

  We agree that such an analysis would be worthwhile, but it is outside the scope of this paper. See main response.

        127 of course, both the univariate and the multivariate models could be made hierarchical. Not 100% clear why you only choose to make the multivariate model hierarchical.

  We have clarified here that the "hierarchical" model means "hierarchical multivariate" (line 180). More generally, our hypothesis is that the benefit of hierarchy to trait estimation comes from leveraging the across-PFT covariance structure, which is nonexistent in the univariate model.

        134 Could you comment on whether Gibbs sampling is the most efficient / preferred method for the estimation of covariance matrices in such a setting?

  We have added a sentence about the advantages of Gibbs sampling in terms of its 100% proposal acceptance rate (compared to the 10-65% target acceptance rates of Metropolis Hastings, Differential Evolution, and Hamiltonian Monte-Carlo) (line 191-195). We recognize that this is not a complete picture of the efficiency, since other algorithms could potentially compensate for lower acceptance by achieving faster convergence. A thorough comparison of algorithm efficiency would be useful and interesting, but is outside the scope of this work.

        136 You should specify the parameters, i.e. were all priors uninformative?

        137 Same for the Wishart – was this a more or less uninformative Wishart?

  We added a table containing values for the weakly-informative priors on the multivariate normal distribution to the supplementary information (Tab. S1), and a description of the other priors to this section (lines 210-213).

        138 Estimating covariances is notoriously problematic, in particular in small data situations. It would seem useful to me to spend a few words on the degrees of freedom, scaling, and whether you see an overfitting concern here, plus about possible ideas for Bayesian regularization of the means or covariances (in case of low data situations). If you think that the data is usually so strong that this is not an issue, that’s also fine, but would be good to be explicit about this. Also, I wonder: have you tested (via simulation) that your current setup can faithfully retrieve the correlation parameters?

  We have added a few sentences to the methods describing how our approach avoids overfitting by tending towards zero covariance estimates with wide credible intervals in cases where data are limiting (lines 241-246). Beyond that, given Reviewer 2's comments that this manuscript is "too focused on the technical methods at the expense of the motivating questions", we are reluctant to spend too much time discussing alternative approaches, including Bayesian regularization.

        139 Not sure if this equation is useful to the reader. Is there anything we learn from that? Seems just a restatement of what you said

  We have removed this equation as well as the preceding one (which was similarly uninformative).

        139 Equations should have numbers

  We have added numbers to all equations.

        141 Which page? This is a large book.

  We have added the section number, section title, and page number (line 207-208).

        142 I don’t understand why this would be the case. Can you explain why you couldn’t model missing observations as latent variables?

  This was unclear wording on our part. What we meant to say here was that the most popular R packages for Bayesian analysis using graphical models (namely, BUGS/JAGS and Stan) do not have convenient support for multivariate distributions with partial missingness. Our model actually does treat the partially missing observations as latent variables -- it just samples them in blocks conditioned on the partially present data in each row and the current sampled mean vector and variance-covariance matrix. We have revised this section to make this clearer (lines 214-237).

        147 The explanation is not 100% clear to me: do I understand correctly: in a loop, you a) impute b) fit the hierarchical model? What I don’t get is: i) how does the fitted model then feed back to the imputation step? Also, when do you stop? I think it would be important to explain this procedure in more detail.

  When we (more correctly) describe our approach as modeling missing values as latent variables (see previous comment), this section should make more sense. However, for clarity, we have added a more detailed step-by-step explanation of the sampling procedure here (lines 227-237). We also refer readers to the detailed (and now, revised and extended) demonstration of the algorithm in Supporting Information Method S1.

        147 Moreover, if this a new method, I would ask you to confirm that this actually works with randomly removed data (it’s clear that imputation will always run in trouble if you remove data purposefully, but at least let’s make sure it works under ideal conditions). Ideal validation would be via <https://arxiv.org/pdf/1804.06788.pdf> , in this case you check the entire analysis chain.

  We have added a section to Supplementary Method S1 that provides a detailed validation of our approach for imputing missing values on simulated bivariate data and the classic Iris dataset.

        150 How many missing values are we talking about here in the real data? 10%, 90%? See comment above, if you check the methods, make sure that the scenario corresponds to what you find in the real data

  We have added the sample sizes for each trait and PFT to Table 1. Information on pairwise missingness and the corresponding estimates of the reduced major axis slope coefficients are shown in Table S4.

        153 Is this the univariate psrf, i.e. per parameter? If so, write: for all parameters

  We have revised this accordingly, clarifying that this is the univariate PSRF for every parameter (line 248).

        160 I realize that it’s inherently difficult to summarize a 7-dim correlation, but just as a comment: would it be possible that, if the first and second largest EV are very close to each other, one could get a large switch of the direction of the dominant EV by a small change in the data, similar to what often happens in PCAs? As a more robust alternative, one could consider similarity measures of the MVN, e.g. KL distance, which would be independent of these axis problems.

  We have replaced this analysis and corresponding figure with one showing the reduced major axis slopes (Fig. 1). This calculation (including the uncertainty propagation) is conceptually much simpler, so we feel this comment no longer applies.

        Fig.3 What you provide here is basically the raw data for the covariance matrix. It’s really hard to see any trends here. Consider if you can somehow compress this to something more meaningful. Also, axis should be properly labeled.

  As mentioned above, we have replaced this figure with a tile plot of reduced major axis slopes (Fig. 1) that, we hope, more clearly shows patterns within- and across PFTs.

        Major comment analysis: all measures you report here are based on the fitted models only (i.e. don’t consider the fit to the data / residuals). I find that somewhat dangerous. What I would ask you to add is some measure if predictive error for all three models (univariate, multivariate, hierarchical multivariate). I think in this case it’s unlikely that you’re grossly overfitting, so it would be OK for me if you would calculate this on the same data that you used for fitting, but more ideal would of course be to have a hold-out. Consider also if there is a possibility to analyze the error, e.g. by plotting / regressing it against suitable predictors such as PFT, taxonomy, location

  See main response.

        200 Here and later: it’s unclear what model you refer to when you say “global” etc. … you introduced three models: univariate, multivariate, and multivariate hierarchical. I assume that you can’t mean the univariate, but with global you could mean the global multivariate, the between PFT correlation in the hierarchical, or the global (within + across PFT) correlation in the hierarchical model.

        226 Maybe I’m missing it, but is there any discussion of the correlation between PFTs? In general, I think you could leverage the hierarchical setup much better. Essentially, what we have is a global correlation. With the hierarchical model, we can now partition this global LES into a within and between PFT correlation. What I understand from this section so far is that the within PFT correlation is broadly identical to the global correlation, except for some PFTs. But what about the between PFT correlation, does this also follow the LES, or is this completely different? Apart from the verbal discussion, it would be great if the partitioning could be visualized in some way, so that one could see where the different PFTs lie in the overall trait spectrum, and how the traits correlate within them. If this could be done, I think it could be an ecologically very valuable figure.

        234 OK, I see this addresses in some sense my point about the correlation across PFTs above, but would be nice to discuss this in terms of correlation of the means, not means only.

  We have completely re-written this section of the results around the new Figure 1 and with a heavier and explicit focus on the across-PFT patterns (section 3.1, throughout).

        233 and which had lower error?

  In the revised results section, this comment no longer applies.

        As a side note: given the small number of PFTs, one does wonder if the trait correlation across PFTs can even properly be estimated (I think you make some comments to this effect later, but if it can’t estimate, then why fit this model?).

  We have added a simple power analysis of correlation coefficients (lines 376-380). The result is that, with 14 PFTs, we can estimate correlations of at least 0.74 with 95% power and confidence. This means that our "non-significant" correlations still allow us to place an upper limit on the strength of across-PFT correlations, albeit a higher one than we would have liked.

        244 significantly? This is a Bayesian analysis.

        268 You use again “significant”, but I don’t think you have run significant tests here. Clarify what you mean

  We have replaced "siginficantly" with more precise text about intersection with the 95% credible interval throughout the text.

        244 how were CLM parameters derived?

  This is described in the "Methods: Analysis of results section" (lines 285-288).

        251 OK, this is the uncertainty of the mean, but more important for me would be the predictive error, which could be very different (also depending on how much IV is in these traits).

  See main response.

        279 It’s a bit unfortunate that this analysis doesn’t allow separating spread and direction of the trade-off. What I mean is that a lower correlation could result from a smaller slope in a regression between two traits, or from more spread around the regression line. Would be nice to see which of the two possibilities is responsible here, a change of the direction of the trade-off, or an increase in variability. Please discuss if applicable.

        282 Again, for building this into models, one would probably be interested in the slope and not R2

        296 Again, I wonder if “weak” means that slope or R2, plus, again: significance. Moreover, note that significance is not effect size.

  As mentioned above, we have replaced the analysis of correlations with analysis of reduced major axis slopes, which make this distinction possible.

        316 The logical conclusions seems to examine other groups than the standard model PFTs, e.g. divide species taxonomically, morphologically, or via biomes

  We have added a sentence about this as a future direction later in the discussion (line 584-587).

        331 This is a weird wording, at least you should use predictive uncertainty, but I’m not even sure if you showed this. What you seem to discuss here is a reduction of posterior predictive uncertainty, but that is just an estimate. I can reduce posterior predictive uncertainty just by adjusting the prior, but that does’t mean that the model will better fit the data. I think you urgently need to establish a measure of model fit / predictive error for this discussion.

        335 but again, a change doesn’t imply an improvement. You have to show that the multivariate model is better

  First of all, we have revised this wording to be more precise ("posterior predictive uncertainty", line 555). Second, while it is technically true that the posterior predictive uncertainty can be reduced by tweaking the prior, that is not the case in our analysis because all three models used the same priors (on corresponding terms; e.g. variance priors in univariate model were the same as diagonals of covariance matrix priors in multivariate models). Finally, and most importantly, we have added the RMSE analysis requested here -- see main response.

### 2019-09-09 AppendixS1.tex
Fix Appendix S1 formatting.

% Created 2019-09-09 Mon 08:53
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[backend=biber,style=authoryear,date=year]{biblatex}
\addbibresource{/Users/shik544/Dropbox/references/library.bib}
\input{authors.tex}
\usepackage{hanging}
\date{}
\title{Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis}
\hypersetup{
 pdfauthor={},
 pdftitle={Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.3)}, 
 pdflang={English}}
\begin{document}

@@

\section*{Appendix S1: References for the original sources of the TRY trait data used in our analysis.}

\begin{hangparas}{1.5em}{1}\hypertarget{citeproc_bib_item_1}{Adler, P. B., D. G. Milchunas, W. K. Lauenroth, O. E. Sala, and I. C. Burke. 2004. Functional Traits of Graminoids in Semi-Arid Steppes: a Test of Grazing Histories. Journal of Applied Ecology 41:653–663.}

\hypertarget{citeproc_bib_item_2}{Adriaenssens, S. 2012. Dry deposition and canopy exchange for temperate tree species under high nitrogen deposition.}

\hypertarget{citeproc_bib_item_3}{Akhmetzhanova, A. A., N. A. Soudzilovskaia, V. G. Onipchenko, W. K. Cornwell, V. A. Agafonov, I. A. Selivanov, and J. H. C. Cornelissen. 2012. A Rediscovered Treasure: Mycorrhizal Intensity Database for 3000 Vascular Plant Species Across the Former Soviet Union. Ecology 93:689–690.}

\hypertarget{citeproc_bib_item_4}{Araujo, A. de, J. Ometto, A. Dolman, B. Kruijt, M. Waterloo, and J. Ehleringer. 2012. LBA-ECO CD-02 C and N Isotopes in Leaves and Atmospheric CO2, Amazonas, Brazil. ORNL Distributed Active Archive Center.}

\hypertarget{citeproc_bib_item_5}{Atkin, O. K., M. Schortemeyer, N. McFarlane, and J. R. Evans. 1999. The Response of Fast- and Slow-Growing Acacia Species To Elevated Atmospheric CO2: An Analysis of the Underlying Components of Relative Growth Rate. Oecologia 120:544–554.}

\hypertarget{citeproc_bib_item_6}{Auger, S., and B. Shipley. 2012. Inter-Specific and Intra-Specific Trait Variation Along Short Environmental Gradients in an Old-Growth Temperate Forest. Journal of Vegetation Science 24:419–428.}

\hypertarget{citeproc_bib_item_7}{Bakker, C., J. Rodenburg, and P. M. van Bodegom. 2005. Effects of Ca- and Fe-Rich Seepage on P Availability and Plant Performance in Calcareous Dune Soils. Plant and Soil 275:111–122.}

\hypertarget{citeproc_bib_item_8}{Bakker, C., P. M. Van Bodegom, H. J. M. Nelissen, W. H. O. Ernst, and R. Aerts. 2006. Plant Responses To Rising Water Tables and Nutrient Management in Calcareous Dune Slacks. Plant Ecology 185:19–28.}

\hypertarget{citeproc_bib_item_9}{Baraloto, C., C. E. T. Paine, L. Poorter, J. Beauchene, D. Bonal, A.-M. Domenach, B. Hérault, S. Patiño, J.-C. Roggy, and J. Chave. 2010. Decoupled Leaf and Stem Economics in Rain Forest Trees. Ecology Letters 13:1338–1347.}

\hypertarget{citeproc_bib_item_10}{Beckmann, M., M. Hock, H. Bruelheide, and A. Erfmeier. 2012. The Role of UV-B Radiation in the Invasion of Hieracium pilosella-A Comparison of German and New Zealand Plants. Environmental and Experimental Botany 75:173–180.}

\hypertarget{citeproc_bib_item_11}{Blonder, B., V. Buzzard, I. Simova, L. Sloat, B. Boyle, R. Lipson, B. Aguilar-Beaucage, A. Andrade, B. Barber, C. Barnes, and et al. 2012. The Leaf-Area Shrinkage Effect Can Bias Paleoclimate and Ecology Research. American Journal of Botany 99:1756–1763.}

\hypertarget{citeproc_bib_item_12}{Blonder, B., C. Violle, L. P. Bentley, and B. J. Enquist. 2010. Venation Networks and the Origin of the Leaf Economics Spectrum. Ecology Letters 14:91–100.}

\hypertarget{citeproc_bib_item_13}{Blonder, B., C. Violle, and B. J. Enquist. 2013. Assessing the Causes and Scales of the Leaf Economics Spectrum Using Venation Networks Inpopulus Tremuloides. Journal of Ecology 101:981–989.}

\hypertarget{citeproc_bib_item_14}{Bocanegra, K., F. Fernández, and J. Galvis. 2015. Grupos Funcionales De Árboles En Bosques Secundarios De La Región Bajo Calima (Buenaventura, Colombia). Boletín Científico. Centro de Museos. Museo de Historia Natural 19:17–40.}

\hypertarget{citeproc_bib_item_15}{Bodegom, P. M. van, B. K. Sorrell, A. Oosthoek, C. Bakker, and R. Aerts. 2008. Separating the Effects of Partial Submergence and Soil Oxygen Demand on Plant Physiology. Ecology 89:193–204.}

\hypertarget{citeproc_bib_item_16}{Bond-Lamberty, B., S. T. Gower, C. Wang, P. Cyr, and H. Veldhuis. 2006. Nitrogen Dynamics of a Boreal Black Spruce Wildfire Chronosequence. Biogeochemistry 81:1–16.}

\hypertarget{citeproc_bib_item_17}{Bond-Lamberty, B., C. Wang, S. T. Gower, and J. Norman. 2002a. Leaf Area Dynamics of a Boreal Black Spruce Fire Chronosequence. Tree Physiology 22:993–1001.}

\hypertarget{citeproc_bib_item_18}{Bond-Lamberty, B., C. Wang, and S. T. Gower. 2002b. Aboveground and Belowground Biomass and Sapwood Area Allometric Equations for Six Boreal Tree Species of Northern Manitoba. Canadian Journal of Forest Research 32:1441–1450.}

\hypertarget{citeproc_bib_item_19}{Bond-Lamberty, B., C. Wang, and S. T. Gower. 2004. Net Primary Production and Net Ecosystem Production of a Boreal Black Spruce Wildfire Chronosequence. Global Change Biology 10:473–487.}

\hypertarget{citeproc_bib_item_20}{Brown, K. A., D. F. B. Flynn, N. K. Abram, J. C. Ingram, S. E. Johnson, and P. Wright. 2011. Assessing Natural Resource Use By Forest-Reliant Communities in Madagascar Using Functional Diversity and Functional Redundancy Metrics. PLoS ONE 6:e24107.}

\hypertarget{citeproc_bib_item_21}{Burrascano, S., R. Copiz, E. Del Vico, S. Fagiani, E. Giarrizzo, M. Mei, A. Mortelliti, F. M. Sabatini, and C. Blasi. 2015. Wild Boar Rooting Intensity Determines Shifts in Understorey Composition and Functional Traits. Community Ecology 16:244–253.}

\hypertarget{citeproc_bib_item_22}{Butterfield, B. J., and J. M. Briggs. 2010. Regeneration Niche Differentiates Functional Strategies of Desert Woody Plant Species. Oecologia 165:477–487.}

\hypertarget{citeproc_bib_item_23}{Byun, C., S. de Blois, and J. Brisson. 2012. Plant Functional Group Identity and Diversity Determine Biotic Resistance To Invasion By an Exotic Grass. Journal of Ecology 101:128–139.}

\hypertarget{citeproc_bib_item_24}{Campbell, C., L. Atkinson, J. Zaragoza-Castells, M. Lundmark, O. Atkin, and V. Hurry. 2007. Acclimation of Photosynthesis and Respiration Is Asynchronous in Response To Changes in Temperature Regardless of Plant Functional Group. New Phytologist 176:375–389.}

\hypertarget{citeproc_bib_item_25}{Campetella, G., Z. Botta-Dukát, C. Wellstein, R. Canullo, S. Gatto, S. Chelli, L. Mucina, and S. Bartha. 2011. Patterns of Plant Trait-Environment Relationships Along a Forest Succession Chronosequence. Agriculture, Ecosystems \& Environment 145:38–48.}

\hypertarget{citeproc_bib_item_26}{Carswell, F. E., P. Meir, E. V. Wandelli, L. C. M. Bonates, B. Kruijt, E. M. Barbosa, A. D. Nobre, J. Grace, and P. G. Jarvis. 2000. Photosynthetic Capacity in a Central Amazonian Rain Forest. Tree Physiology 20:179–186.}

\hypertarget{citeproc_bib_item_27}{Cavender-Bares, J., A. Keen, and B. Miles. 2006. Phylogenetic Structure of Floridian Plant Communities Depends on Taxonomic and Spatial Scale. Ecology 87:S109–S122.}

\hypertarget{citeproc_bib_item_28}{Cerabolini, B. E. L., G. Brusa, R. M. Ceriani, R. De Andreis, A. Luzzaro, and S. Pierce. 2010. Can CSR Classification Be Generally Applied Outside Britain? Plant Ecology 210:253–261.}

\hypertarget{citeproc_bib_item_29}{Chambers, J. Q., E. S. Tribuzy, L. C. Toledo, B. F. Crispim, N. Higuchi, J. d. Santos, A. C. Araújo, B. Kruijt, A. D. Nobre, and S. E. Trumbore. 2004. Respiration From a Tropical Forest Ecosystem: Partitioning of Sources and Low Carbon Use Efficiency. Ecological Applications 14:72–88.}

\hypertarget{citeproc_bib_item_30}{Chen, Y., W. Han, L. Tang, Z. Tang, and J. Fang. 2011. Leaf Nitrogen and Phosphorus Concentrations of Woody Plants Differ in Responses To Climate, Soil and Plant Growth Form. Ecography 36:178–184.}

\hypertarget{citeproc_bib_item_31}{Choat, B., S. Jansen, T. J. Brodribb, H. Cochard, S. Delzon, R. Bhaskar, S. J. Bucci, T. S. Feild, S. M. Gleason, U. G. Hacke, and et al. 2012. Global Convergence in the Vulnerability of Forests To Drought. Nature 491:752–755.}

\hypertarget{citeproc_bib_item_32}{Cornelissen, J. H. C. 1996. An Experimental Comparison of Leaf Decomposition Rates in a Wide Range of Temperate Plant Species and Types. The Journal of Ecology 84:573.}

\hypertarget{citeproc_bib_item_33}{Cornelissen, J. H. C., P. C. Diez, and R. Hunt. 1996. Seedling Growth, Allocation and Leaf Attributes in a Wide Range of Woody Plant Species and Types. The Journal of Ecology 84:755.}

>>>>

% Created 2019-09-09 Mon 09:26
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[backend=biber,style=authoryear,date=year]{biblatex}
\addbibresource{/Users/shik544/Dropbox/references/library.bib}
\input{authors.tex}
\date{}
\title{Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis}
\hypersetup{
 pdfauthor={},
 pdftitle={Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.3)}, 
 pdflang={English}}
\begin{document}

@@

\noindent
\textbf{Appendix S1:} References for the original sources of the TRY trait data used in our analysis.

\vspace{\baselineskip}

\nocite{kleyer_2008_leda_traitbase}

\nocite{wirth_2009_imprint}

\nocite{baraloto_2010_decoupled}

\nocite{craine_2009_global}

\nocite{veihmeyer_1956_soil_moisture}

\nocite{cerabolini_2010_can}

\nocite{wright_2010_functional}

\nocite{wright_2004_worldwide}

\nocite{ogaya_2003_comparative}

\nocite{akhmetzhanova_2012_rediscovered_treasure}

\nocite{frenette-dussault_2011_functional}

\nocite{medlyn_1999_effects}

\nocite{kattge_2009_quantifying}

\nocite{laughlin_2011_climatic}

\nocite{campetella_2011_patterns}

\nocite{auger_2012_inter}

\nocite{fyllas_2009_basin}

\nocite{blonder_2012_leaf}

\nocite{cornelissen_2003_functional}

\nocite{cavender-bares_2006_phylogenetic}

\nocite{garnier_2007_assessing}

\nocite{prentice_2010_evidence}

\nocite{brown_2011_assessing}

\nocite{schweingruber_2005}

\nocite{onoda_2011_global}

\nocite{han_2005_leaf}

\nocite{domingues_2010_co}

\nocite{han_2005_leaf}

\nocite{messier_2010_how}

\nocite{price_2007_scaling}

\nocite{kraft_2008_functional}

\nocite{pierce_2013_allocating}

\nocite{wright_2006_relationships}

\nocite{reich_2008_scaling}

\nocite{domingues_2013_seasonal}

\nocite{niinemets_2001_global}

\nocite{cornwell_2008_plant}

\nocite{vergutz_2012_global}

\nocite{sandel_2011_using}

\nocite{poorter_2009_causes}

\nocite{gallagher_2012_global}

\nocite{williams_2012_lba}

\nocite{choat_2012_global}

\nocite{fonseca_2000_shifts}

\nocite{burrascano_2015_wild}

\nocite{milla_2011_multi}

\nocite{adriaenssens_2012_dry}

\nocite{willis_2009_phylogenetic}

\nocite{kisel_2012_testing}

\nocite{pierce_2012_combined}

\nocite{cornelissen_1996_experimental}

\nocite{yguel_2011_phytophagy}

\nocite{xu_2003_seasonal}

\nocite{bond-lamberty_2004_net}

\nocite{von_2004_testing}

\nocite{chen_2011_leaf}

\nocite{byun_2012_plant}

\nocite{laughlin_2011_climatic}

\nocite{ordonez_2010_plant}

\nocite{kerkhoff_2006_phylogenetic}

\nocite{butterfield_2010_regeneration}

\nocite{bond-lamberty_2002_aboveground}

\nocite{pierce_2007_disturbance}

\nocite{gutierrez_2012_successional}

\nocite{manzoni_2013_optimization}

\nocite{wright_2012_does}

\nocite{chambers_2004_respiration}

\nocite{guerin_2012_leaf}

\nocite{bond-lamberty_2002_leaf}

\nocite{mueller_2006_plant}

\nocite{cerabolini_2010_can}

\nocite{craine_2011_functional}

\nocite{craine_2012_community}

\nocite{shipley_2002_trade}

\nocite{wohlfahrt_1999_inter}

\nocite{rueger_2011_determinants}

\nocite{rueger_2009_response}

\nocite{quested_2003_decomposition}

\nocite{choat_2012_global}

\nocite{pahl_2013_no}

\nocite{shipley_2002_dry}

\nocite{minden_2011_testing}

\nocite{meir_2002_acclimation}

\nocite{schererlorenzen_2007_exploring}

\nocite{bakker_2006_plant}

\nocite{penuelas_2009_faster}

\nocite{powers_2010_plant}

\nocite{shiodera_2008_variation}

\nocite{fitter_1994_ecological_flora_database}

\nocite{minden_2012_plant}

\nocite{bond-lamberty_2006_nitrogen}

\nocite{rueger_2011_determinants}

\nocite{peco_2005_effect}

\nocite{tucker_2011_physiological}

\nocite{weedon_2009_global}

\nocite{blonder_2010_venation}

\nocite{spasojevic_2012_inferring}

\nocite{campbell_2007_acclimation}

\nocite{craven_2007_between}

\nocite{cornelissen_2004_leaf}

\nocite{pillar_2003_improved}

\nocite{hickler_1999_plant}

\nocite{bakker_2005_effects}

\nocite{vile_2005_significations}

\nocite{craine_2005_environmental}

\nocite{swaine_2007_ecological_bornean}

\nocite{wilson_2000_spatial}

\nocite{preston_2006_wood}

\nocite{zapata-cuartas_2012_probability}

\nocite{blonder_2013_assessing}

\nocite{blonder_2010_venation}

\nocite{guy_2013_limited}

\nocite{kichenin_2013_contrasting}

\nocite{louault_2005_plant}

\nocite{araujo_2012_lba}

\nocite{bocanegra_2015_grupos}

\nocite{beckmann_2012_role}

\nocite{adler_2004_functional}

\nocite{loveys_2003_thermal}

\nocite{bodegom_2008_separating}

\nocite{domingues_2013_seasonal}

\nocite{shipley_2000_functional}

\nocite{loranger_2012_predicting}

\nocite{pyankov_1999_leaf}

\nocite{shipley_1995_structured}

\nocite{cornelissen_1996_seedling}

\nocite{carswell_2000_photosynthetic}

\nocite{givnish_2004_adaptive}

\nocite{meziane_1999_interacting}

\nocite{meir_2007_photosynthetic}

\nocite{atkin_1999_response}

\nocite{diaz_2004_plant}

\nocite{kazakou_2006_co}

\nocite{demey_2013_nutrient}

\printbibliography[heading=none]
\end{document}
